spatial_figures

### 2025-01-17 spatial_figs.Rmd
few minor site map updates

@@

p_cols <- ggplot(catchment_mo2, aes(x = month_name, y = precip_mean,
                                    color = site, fill = site)) +
  geom_col(position = 'dodge') +
  geom_errorbar(aes(ymin = 0, ymax = precip_mean + precip_sd), 
                position = position_dodge(width = 0.6), width = 0.2) +
  scale_color_manual(values = c("blue", "orange"),
                     labels = c("Gridded", "Observed")) +  # Rename color legend items
  scale_fill_manual(values = c("blue", "orange"),
                    labels = c("Gridded", "Observed")) +   # Rename fill legend items
  theme_bw(base_size = 12) +
  labs(y = 'Precipitation (mm)',
       x = element_blank()) +
  guides(color = guide_legend(title = NULL),
         fill = guide_legend(title = NULL))

>>>>

dem_raster1 <- rast(dem_raster)

# extract min, max
min <- terra::extract(dem_raster1, hru_new, 'min', touches=T)
min(min$layer)

max <- terra::extract(dem_raster1, hru_new, 'max', touches=T)
max(max$layer)

@@

p_cols <- ggplot(catchment_mo2, aes(x = month_name, y = precip_mean,
                                    color = site, fill = site)) +
  geom_col(position = 'dodge') +
  geom_errorbar(aes(ymin = 0, ymax = precip_mean + precip_sd), 
                position = position_dodge(width = 0.6), width = 0.2) +
  scale_color_manual(values = c("blue", "orange"),
                     labels = c("Gridded", "Observed")) +  # Rename color legend items
  scale_fill_manual(values = c("blue", "orange"),
                    labels = c("Gridded", "Observed")) +   # Rename fill legend items
  theme_bw(base_size = 20) +
  labs(y = 'Precipitation (mm)',
       x = element_blank()) +
  guides(color = guide_legend(title = NULL),
         fill = guide_legend(title = NULL)) +
    theme(
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    strip.text = element_blank()
  )
